---
title: "**Factor relevelling example**"
subtitle: |
  | A Practical Foray into Lengthy Subtitle Management, Iris Dataset Tampering, 
  | and the Unceasing Pursuit of Stakeholder-Friendly Data Presentation.
  | From Markdown Mastery to Factor Finagling
author: 
  name: "Márton Kiss MD"
committee:
  - name: Márton Kiss MD
    position: Applied Biostatistician
date: 4242.42.42.
number_Sections: yes
sign_page: true
output:
  pagedown::thesis_paged: 
    # # DO NOT overwrite the default css-s! Breaks the pagination
    #  - default-fonts
    #  - default-page
    #  - styles.css
    #css:
    lof: true
    lot: true
    toc: true
    toc-title: Contents
    template:
      template_pdflike.html
  html_document:
    df_print: paged
    keep_tex: yes
    fig_caption: yes
    toc: no
    css: styles.css
bibliography: packages.bib # Causes crash??
link-citations: yes
---

```{r setup, include=FALSE, warning = FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      fig.align = 'center',
                      warning = FALSE,
                      message = FALSE)
```

# Summary {.chapter}

This is a lightweight document for me to kink out the particulars of producing serious-looking but verstile documents. Rendering for 10 minutes would be unpalatable for this document, however I wanted it to serve some useful purpose besides flaunting my template.


# Relevelling & *Forcats* {.chapter}

Factors sometimes get on my nerve. Their levels' order keep changing, you want to switch between human readable (stakeholder readable) and easy-to-type names, etc.

Take a look at the *'iris'* dataset. Species is clearly a factor.


```{r, comment='', results='asis'}

unique(iris$Species)

```

Lets rename some species. The below code is a bit bloated but intuitive IMHO.

```{r}
library(dplyr)

iris_recode <- iris %>%
  mutate(Species_hr = 
           forcats::fct_recode( Species, 
                                 smelly = as.character(unique(iris$Species)[1]),
                                 fluffy = as.character(unique(iris$Species)[2])
                                 #Didn't recode 'virginica' asan example
                                 ))
```

And to test the results, lets see what a printout would say. Can I reference said table? Lets try (\@ref(tab:atable)):

```{r atable}

set.seed(12345)

iris_recode %>%
  .[sort(sample(nrow(.),10)),] %>% 
    knitr::kable(label = "atable",
                 # NEEDS both label and caption for referencing
                 caption = "Example cases from the recoded table")

```



# Notes

Information regarding the compilation of this document:

<!---
Example of printing chunk stuff without the hideous '##' 
--->

```{r, comment='', results='asis'}
knitr::opts_chunk$set(comment = NA)
sessionInfo() %>% report::report() %>% cat()
```

This document was compiled at:

```{r last_chunk}

Sys.time()
save.image(file = here::here("inst","states","cookbook_out.Rdata"))

```


# Appendix

This is how put all your code into an appendix.

```{r}
#| ref.label=knitr::all_labels(),
#| echo=TRUE,
#| eval=FALSE

# This throws a warning everytime so lets forget about it
#| tidy=TRUE

```
